Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-19 prop_letter.tex
prop_letter.tex Change non-breaking space setting...
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}

@@

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}.  For example,
Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
continues on whether contextuality is experimentally
verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum
mechanics that are intrinsically, rather than only implicitly,
consistent with the resources available for the realistic accuracy of
an actual measurement.

Our first observation is that essential objectives of our program to
achieve a computable theory of quantum mechanics and finite-resource
measurement, attempted previously with computable number
systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical interval-valued probability
measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
axiomatizing a quantum interval-valued probability measure (QIVPM)
framework exploiting the fact that a density matrix approach can be
considered as equivalent to a description of quantum states using
probability measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
One result is that the expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude that
they correspond to the limit of an infinite number of precise
intervals, and the set of crypto-deterministic intervals (the set~$\{\imposs,\necess\}$),
respectively.

@@

% Textbook quantum mechanics asserts that the probability of a
% measurement can be computed from wave function of the system and the
% measuring observable \emph{exactly} while real measurements must be
% finite precision.  Whether finite precision measurement in reality
% affect the idealized quantum concept, e.g.,
% contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
% and the very foundation of quantum mechanics is still a problem. In
% this letter, we model the finite precision quantum measurement by
% quantum interval-valued probability measures (IVPMs) which provides
% not only a uniform framework to understand Gleason's
% theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
% Kochen-Specker
% theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
% but also some examples which cannot be explained by the Born
% rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.

% The tension between finite precision measurement and the foundation of
% quantum mechanics sharpened, when the original definition of
% contextuality based on infinitely precise numbers is proved not
% experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.  After a
% long debate~\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
% still trying to update the definition of contextuality when they want
% to perform further
% experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

% We found that finite precision measurement affects not only
% contextuality but also the fundamental rule computing probability from
% a state.  In the early formulation of quantum mechanics, von Neumann
% essentially formulated a quantum state as a density matrix while
% Mackey formulated a quantum state as a quantum probability measure
% which are proved by Gleason to be the essentially same as a density
% matrix~\cite{Varadarajan2008}.  Combining quantum probability measures
% and the classical IVPM~\cite{JamisonLodwick2004} which could be used
% to formulate classical finite precision measurement, we can define
% quantum IVPMs. Surprisingly, there is a quantum IVPM which cannot be
% compatible with any density matrix according to the Born rule. Similar
% to revising the definition of contextuality because of finite
% precision measurement, the very basic definition of a quantum state or
% how to compute the probability from a state might need to be refined
% when we consider the finite precision measurement. This can also
% provide a new quantum phenomena different from the classical world,
% because IVPMs become classical so that the non-Born IVPMs disappears
% when we restricting the domain of quantum IVPMs on a commuting
% sub-event space.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events~\cite{Kolmogorov1950}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection~$\mathbb{0}$, the identity
projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ such
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ such $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped using a probability measure
$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$ subject to
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\textrm{.}\label{eq:QuantumProbability-Addition}
\end{equation}

@@

% In conventional quantum theory (CQT), when we measure a property
% $\mathbf{O}$ of a physical system whose state is represented by a
% density matrix~$\rho$, the probability to obtain the value $\lambda$
% of that property is determined by the Born rule
% $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
%   P_{i}\right)$, where $P_{i}$ denotes the projector onto the
% eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
% Hermitian operator
% $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
% Alternatively, one may say that the state $\rho$ determines the
% probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
% from the set $\events$ of all possible projectors $P$ onto the
% interval $[0,1]$, and satisfies the following probability axioms~
% \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:

% \begin{itemize}
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
% \item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
% 1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
% \item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_iP_j=\delta_{ij}P_i$,
% we have 
% \begin{equation}
% \mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
% \sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
% \textrm{ .}\label{eq:QuantumProbability-Addition}
% \end{equation}
% \end{itemize}
% Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
% satisfying the above axioms, Gleason's theorem asserts that there
% exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
% in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

% Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
% decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
% value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
% \begin{equation}
% \expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
% \end{equation}

% To formalize the idea of finite precision measurement, we next
% introduce the notion of quantum interval-valued probability measures
% (\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
% interval $[0,1]$ by a finite collection $\mathscr{I}$ of
% intervals. Since the intervals $\imposs=\left[0,0\right]$ and
% $\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
% arithmetic operations on intervals
% satisfy \begin{subequations}\label{eq:interval-operations}
% \begin{eqnarray}
%  &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
%  &  & x[l,r]=\begin{cases}
% [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
% [xr,xl] & \textrm{for }x\le0\textrm{ .}
% \end{cases}
% \end{eqnarray}
% \end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
% defined by the axioms: 
% \begin{itemize}
% \item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
% \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
% \item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
% \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
% \begin{equation}
% \bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
% \end{equation}
% \end{itemize}
% condition that provides only a bound and not an equivalence as in
% Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
% $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
% $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
% \[
% \bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
% \]

@@

We will start by reviewing IVPMs in the classical setting~\cite{JamisonLodwick2004}
and then propose our quantum generalization. In the classical setting,
there are several proposals for ``imprecise probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Grabisch2016}.''
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event $E$ is generalized
from a single real number to an interval of certainty $[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence
for the event and $r$ corresponds to the strength of evidence against
the event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

First for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space).
For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the complement
event. For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition as
follows. For general, non-necessarily disjoint events $E_1$ and $E_2$,
we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

\begin{definition}[QIVPM]
  Given a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
  [xr,x\ell] & \textrm{for }x\le0\textrm{ ,}
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
  (projection operator) subject to the following constraints:
  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  we have:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints are the direct counterpart of the
corresponding ones for conventional probability measures. With the
understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
a direct counterpart of Eq.~\ref{eq:classicalconvex}.

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state~$\rho$ is consistent with $\bar{\mu}$ on
a projector~$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the
Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}.  For example,
Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}, and discussion
continues on whether contextuality is experimentally
verifiable\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum
mechanics that are intrinsically, rather than only implicitly,
consistent with the resources available for the realistic accuracy of
an actual measurement.

Our first observation is that essential objectives of our program to
achieve a computable theory of quantum mechanics and finite-resource
measurement, attempted previously with computable number
systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical interval-valued probability
measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by
axiomatizing a quantum interval-valued probability measure (QIVPM)
framework exploiting the fact that a density matrix approach can be
considered as equivalent to a description of quantum states using
probability measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
One result is that the expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude that
they correspond to the limit of an infinite number of precise
intervals, and the set of crypto-deterministic intervals (the set\nb$\{\imposs,\necess\}$),
respectively.

@@

% Textbook quantum mechanics asserts that the probability of a
% measurement can be computed from wave function of the system and the
% measuring observable \emph{exactly} while real measurements must be
% finite precision.  Whether finite precision measurement in reality
% affect the idealized quantum concept, e.g.,
% contextuality\nb\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
% and the very foundation of quantum mechanics is still a problem. In
% this letter, we model the finite precision quantum measurement by
% quantum interval-valued probability measures (IVPMs) which provides
% not only a uniform framework to understand Gleason's
% theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
% Kochen-Specker
% theorem\nb\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
% but also some examples which cannot be explained by the Born
% rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.

% The tension between finite precision measurement and the foundation of
% quantum mechanics sharpened, when the original definition of
% contextuality based on infinitely precise numbers is proved not
% experimental verifiable\nb\cite{PhysRevLett.83.3751,Kent1999}.  After a
% long debate\nb\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
% still trying to update the definition of contextuality when they want
% to perform further
% experiments\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

% We found that finite precision measurement affects not only
% contextuality but also the fundamental rule computing probability from
% a state.  In the early formulation of quantum mechanics, von Neumann
% essentially formulated a quantum state as a density matrix while
% Mackey formulated a quantum state as a quantum probability measure
% which are proved by Gleason to be the essentially same as a density
% matrix\nb\cite{Varadarajan2008}.  Combining quantum probability measures
% and the classical IVPM\nb\cite{JamisonLodwick2004} which could be used
% to formulate classical finite precision measurement, we can define
% quantum IVPMs. Surprisingly, there is a quantum IVPM which cannot be
% compatible with any density matrix according to the Born rule. Similar
% to revising the definition of contextuality because of finite
% precision measurement, the very basic definition of a quantum state or
% how to compute the probability from a state might need to be refined
% when we consider the finite precision measurement. This can also
% provide a new quantum phenomena different from the classical world,
% because IVPMs become classical so that the non-Born IVPMs disappears
% when we restricting the domain of quantum IVPMs on a commuting
% sub-event space.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events\nb\cite{Kolmogorov1950}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection\nb$\mathbb{0}$, the identity
projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ such
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ such $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped using a probability measure
$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$ subject to
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\textrm{.}\label{eq:QuantumProbability-Addition}
\end{equation}

@@

% In conventional quantum theory (CQT), when we measure a property
% $\mathbf{O}$ of a physical system whose state is represented by a
% density matrix\nb$\rho$, the probability to obtain the value $\lambda$
% of that property is determined by the Born rule
% $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
%   P_{i}\right)$, where $P_{i}$ denotes the projector onto the
% eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
% Hermitian operator
% $\mathbf{O}$\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
% Alternatively, one may say that the state $\rho$ determines the
% probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
% from the set $\events$ of all possible projectors $P$ onto the
% interval $[0,1]$, and satisfies the following probability axioms\nb
% \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:

% \begin{itemize}
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
% \item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
% 1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
% \item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_iP_j=\delta_{ij}P_i$,
% we have 
% \begin{equation}
% \mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
% \sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
% \textrm{ .}\label{eq:QuantumProbability-Addition}
% \end{equation}
% \end{itemize}
% Conversely, given any quantum probability measure\nb$\mu:\events\rightarrow[0,1]$
% satisfying the above axioms, Gleason's theorem asserts that there
% exists a unique state\nb$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
% in a Hilbert space of dimension $d\geq3$\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

% Furthermore, if we express an observable\nb$\mathbf{O}$ as its spectrum
% decomposition\nb$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
% value of $\mathbf{O}$ is given by\nb\cite{peres1995quantum,544199,Jaeger2007}
% \begin{equation}
% \expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
% \end{equation}

% To formalize the idea of finite precision measurement, we next
% introduce the notion of quantum interval-valued probability measures
% (\emph{IVPMs})\nb$\bar{\mu}$. The latter replaces the infinitely precise
% interval $[0,1]$ by a finite collection $\mathscr{I}$ of
% intervals. Since the intervals $\imposs=\left[0,0\right]$ and
% $\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
% arithmetic operations on intervals
% satisfy \begin{subequations}\label{eq:interval-operations}
% \begin{eqnarray}
%  &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
%  &  & x[l,r]=\begin{cases}
% [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
% [xr,xl] & \textrm{for }x\le0\textrm{ .}
% \end{cases}
% \end{eqnarray}
% \end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
% defined by the axioms: 
% \begin{itemize}
% \item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
% \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
% \item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
% \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
% $P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
% \begin{equation}
% \bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
% \end{equation}
% \end{itemize}
% condition that provides only a bound and not an equivalence as in
% Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
% $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
% $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
% \[
% \bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
% \]

@@

We will start by reviewing IVPMs in the classical setting\nb\cite{JamisonLodwick2004}
and then propose our quantum generalization. In the classical setting,
there are several proposals for ``imprecise probabilities\nb\cite{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Grabisch2016}.''
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event $E$ is generalized
from a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence
for the event and $r$ corresponds to the strength of evidence against
the event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

First for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space).
For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the complement
event. For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event\nb$E$, we may conclude that
$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition as
follows. For general, non-necessarily disjoint events $E_1$ and $E_2$,
we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

\begin{definition}[QIVPM]
  Given a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
  [xr,x\ell] & \textrm{for }x\le0\textrm{ ,}
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
  (projection operator) subject to the following constraints:
  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  we have:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints are the direct counterpart of the
corresponding ones for conventional probability measures. With the
understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of projection operators\nb\cite{Griffiths2003}, the last
condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
a direct counterpart of Eq.~\ref{eq:classicalconvex}.

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

Quantum IVPMs become classical IVPMs when the space of events includes
only mutually commuting sub-events, where $\events'\subseteq\events$
is called a sub-event space if it satisfies the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection\nb$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For each pair of orthogonal projections\nb$P_0 \in \events'$ and
  $P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
\end{itemize}
